\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-17 WOOT/Files/countermeasure.tex
[countermeasure] a comment
add figures, add new counter measure

\section{Countermeasures}
\label{sec:countermeasures}
Authorization mechanism like GoodUSB\cite{tian2015defending} has been proposed as a countermeasure against BadUSB attack. But as mentioned in Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on internal display to request for authorization, which can be hijacked by our \tool. Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but no defense at all for our \tool. Here we discuss some effective countermeasures against \tool.

@@

\textbf{Detection Based on Processor Status.}
Proposed by Meng et al., JFCGuard\cite{MENG2018252} is a detection mechanism of Juice Filming attack. This is based on the fact that video output will increase the usage of both GPU/CPU. As both Juice Filming attack and our \tool  highly relies on the video stream hijacking.  Thus, in a similar way, we can monitor the usage of processors and adapt a statistic model to tell whether the host device is under \tool attack. Comparing to the external hardware authorization plan, this does not require extra hardware and is more transparent to users. We have assessed this defense in Section~\ref{sec:experiment} and experiments proves this is a promising mechanism\hongyi{EXPERIMENT!!!!!!!!!!}.

>>>>

\section{Countermeasures}
\yechang{Feng Liang says Andriod or iOS can provide an API to render private information only on onboard screen (like iPad OS)}

\label{sec:countermeasures}
Authorization mechanism like GoodUSB\cite{tian2015defending} has been proposed as a countermeasure against BadUSB attack. But as mentioned in Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on internal display to request for authorization, which can be hijacked by our \tool. Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but no defense at all for our \tool. Here we discuss some effective countermeasures against \tool.

@@

\textbf{Isolated UI Rendering}
During our experiment, we noticed that \tool is actually unable to redirect out the locking screen keyboard from the iPad OS. Instead, the keyboard is only available on the internal display. However, this defense is only enabled on the locking screen keyboard, other virtual keyboard is still vulnerable to our \tool. This mechanism has inspired us to propose a new defense against our \tool. If the OS provider like Apple/Google can implement a more generalized \emph{isolated UI rendering} that allows developer to decide whether a content is ``sensitive'' and where it should be rendered. To better illustrate this countermeasure idea, we drew the Figure~\ref{fig:isolated_ui}. In that figure, the password keyboard is set to be ``sensitive'' component while the other parts of the UI is not. Thus the renderer will only render the password keyboard on the trusted internal display and prevent untrusted external display like \tool to obtain sensitive data. We believe this is a promising way to defend users from attack like juice filming and our \tool.
\begin{figure}[htbp]
	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
	\caption{Isolated UI Rendering}
	\label{fig:isolated_ui}
\end{figure}

### 2021-01-17 WOOT/Files/related_work.tex
add figures, add new counter measure

Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious U disk devices by analyze temporal characteristics of BadUSB-like attacks. This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering. This causes the typing characteristics of BadUSB devices to be detected.

>>>>

Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyze temporal characteristics of BadUSB-like attacks. This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering. This causes the typing characteristics of BadUSB devices to be detected.
